\section{General description}
	This is the course descriptor for the \emph{Development 5} course.
\\
Development 5 covers a presentation of modern, distributed (over HTTP)
applications which follow the MVC architectural pattern. Given the huge
breadth of usable technologies in the field, we will focus the
implementation on a single stack: ASP.Net Core, Postgresql, and React
over TypeScript.

An important reminder: the course is not meant to be a \emph{build a
website in 16 hours} workshop. This would collide with the philosophy of
the Informatica degree, which aims at giving the foundational tools to
empower students as ongoing learners. For this reason, we will not dive
deeply into the intricacies of a given technology, but only use the
minimum needed to understand the underlying concept(s) and move on. As a
student, it is highly desirable to realize that most likely each of you
will use \emph{different technologies} on the workplace, and will have
to \emph{keep learn new ones}, so focusing on a single language, stack,
or library would do more harm than good.

	\subsection{Relationship with other teaching units}
		This course builds upon the development courses of the first year.	\\		
		Knowledge acquired the course developement 5 is also useful for some of the projects. A word of warning though: projects and development courses are largely independent, so some things that a student learns during the development courses are not used in the projects, some things that a student learns during the development courses are indeed used in the projects, but some things done in the projects are learned within the context of the project and not within the development courses.
