\section*{Attachment 1: Written exam template}
The general shape of a written exam for this course is made up of a series of highly structured open questions.

\paragraph*{Question I: complexity} \ \\

\textbf{General shape of the question:} \textit{Given the following code, what is its (tightest) complexity class using the big-Oh notation?} \ 

\textbf{Grading:} \textit{2 points for correct answer, 0 otherwise.} \ 

\textbf{Associated learning goals:} \texttt{PERF}.

\ \\ 
\paragraph*{Question II: basic data structures (list, queue, stack, hash tables)} \ \\

\textbf{General shape of the question:} \textit{Complete the code below so that it produces the desired result on the specified basic data structure.} \ 

\textbf{Grading:} \textit{2 points for correct answer, 1 point for minor mistakes, 0 otherwise.} \ 

\textbf{Associated learning goals:} \texttt{DS}\textsuperscript{A}.

\ \\ 
\paragraph*{Question III: sorting} \ \\

\textbf{General shape of the question:} \textit{What is the output of the following algorithm if input is ... ? What is the (tightest) complexity class of the algorithm (using the big-Oh notation)?} \ 

\textbf{Grading:} \textit{2 points for correct complexity and output, 1 point for either correct complexity or output, 0 otherwise.} \ 

\textbf{Associated learning goals:} \texttt{SORT}\textsuperscript{A}.

\ \\ 
\paragraph*{Question IV: trees} \ \\

\textbf{General shape of the question:} \textit{Complete the code below so that it produces the desired result (for example, insertion, lookup, traversal, ...) on a tree.} \ 

\textbf{Grading:} \textit{2 points for correct answer, 1 point for minor mistakes, 0 otherwise.} \ 

\textbf{Associated learning goals:} \texttt{REC}\textsuperscript{A}.

\ \\ 
\paragraph*{Question V: graphs} \ \\

\textbf{General shape of the question:} \textit{What does the following algorithm produce? What is the (tightest) complexity class of the algorithm (using the big-Oh notation)?} \ 

\textbf{Grading:} \textit{2 points for correct complexity and output, 1 point for either correct complexity or output, 0 otherwise.} \ 

\textbf{Associated learning goals:} \texttt{GRAPH}\textsuperscript{A}.

\ \\ 



%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{comment}
	\begin{tabular}{|p{3cm}|p{3.5cm}|p{6cm}|}
		\hline
		\textbf{Learning goal} & \textbf{Dublin descriptors} & \textbf{Tested through} \\
		\hline
		\texttt{KNOW} & 1 & Theoretical examination \\
		\hline
		\texttt{IMPL} & 2 & Practical examination \\
		\hline
		\texttt{AN} & 3 & Theoretical examination \\
		\hline
		\texttt{APP} & 2, 3 & Theoretical and practical examination \\
		\hline
	\end{tabular}
	
	\vspace{1cm}

	Dublin-descriptors:
	\begin{enumerate}
		\item Knowledge and understanding
		\item Applying knowledge and understanding
		\item Making judgements
		\item Communication
		\item Learning skills
	\end{enumerate}
\end{comment}